### 2017-12-06 manuscript.rmd
spelling, knit

Siphonophores remain poorly known, in large part because they are fragile and difficult to collect. They have, however, been of great interest for more than 150 years due to their very unique structure and development [@mapstone2014global;@mackie1987siphonophore]. Like many other cnidarians, they are colonial: they grow by incomplete asexual reproduction. Each siphonophore colony arises from a single embryo that forms the protozooid, the first body. A growth zone then arises that asexually produces other genetically identical zooids [@carre1969etude; @carre1991complete; @carre1967; @carre1995ordre]. These zooids are each homologous to a solitary animal, but are physiologically integrated [@totton1965synopsis; @mackie1987siphonophore; @dunn2006evolution]. Siphonophores differ significantly from all other colonial animals in colony structure, development, and the degree to which they are functionally specialized [@Beklemishev1969;@cartwright2010character]. Each zooid is functionally specialized for a particular task (*e.g.*, feeding, reproducing, swimming) (fig. 2) [@dunn2006evolution], and they are arranged in a repeating,  species-specific pattern.

@@

Understanding the unique ecology, morphology, and development of siphonophores requires an understanding of their phylogenetic relationships. The relationship of siphonophores to other hydrozoans has been difficult to resolve [@cartwright2010character; @Cartwright2008kl; @zapata2015phylogenomic], but there has been progress on their internal relationships. A siphonophore phylogeny [@Dunn:2005dy] based on two genes (16S, 18S) from 52 siphonophore taxa advanced serveral long standing questions about siphonophore biology. These include the relationships of the three historically recognised groups, Cystonectae, Physonectae, and Calycophorae. The cystonects were found to be sister to all other siphonophores, while the calycophorans were nested within physonects. The name Codonophora was given to this clade of physonects and calycophorans [@Dunn:2005dy].

Major questions remained after this early work, though. There was, in particular, little support for important deep relationships within Codonophora. Resolving deep relationships within Codonophora is key to resolving the evolution of several traits, including sexual systems (monoecy versus dioecy) or the gain and loss of particular zooids, such as palpons (fig 2). Here we present a broadly sampled phylogenomic analysis of Siphonophora, assessing transcriptomic data from 33 siphonophore species and 10 outgroup species (2 outgroups were subsequently excluded). Using 1,071 genes shared across species, we find strong support for several relationships within the siphonophore phylogeny. Using this phylogeny, we reconstruct the evolutionary history of characters central to their unique biology, including zooid type, life history traits, and habitat.

@@

#Mantle canal SIMMAP Setup
mantle_data = cdata[which(!is.na(cdata$Mantle.Canal)),]
mantle = mantle_data$Mantle.Canal
names(mantle)=rownames(mantle_data)
MantleTree =  drop.tip(ultratree, which(!(ultratree$tip.label %in% names(mantle))))
make.simmap(MantleTree, mantle, nsim = 100, message=FALSE) -> mantle_sim
```

@@

```{r mantle, echo=F, message=F, warning=F,  fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of nectosome"}
#Simmap NECTOSOME
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# nectosome_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(nectosome_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(mantle_sim)
```

>>>>

Siphonophores remain poorly known, in large part because they are fragile and difficult to collect. They have, however, been of great interest for more than 150 years due to their very unique structure and development [@mapstone2014global;@mackie1987siphonophore]. Like many other cnidarians, they are colonial: they grow by incomplete asexual reproduction. Each siphonophore colony arises from a single embryo that forms the protozooid, the first body. A growth zone then arises that asexually produces other genetically identical zooids [@carre1969etude; @carre1991complete; @carre1967; @carre1995ordre]. These zooids are each homologous to a solitary animal, but are physiologically integrated [@totton1965synopsis; @mackie1987siphonophore; @dunn2006evolution]. Siphonophores differ significantly from all other colonial animals in colony structure, development, and the degree to which they are functionally specialized [@Beklemishev1969;@cartwright2010character]. Each zooid is functionally specialized for a particular task (*e.g.*, feeding, reproducing, swimming) (Fig. 2) [@dunn2006evolution], and they are arranged in a repeating,  species-specific pattern.

@@

Understanding the unique ecology, morphology, and development of siphonophores requires an understanding of their phylogenetic relationships. The relationship of siphonophores to other hydrozoans has been difficult to resolve [@cartwright2010character; @Cartwright2008kl; @zapata2015phylogenomic], but there has been progress on their internal relationships. A siphonophore phylogeny [@Dunn:2005dy] based on two genes (16S, 18S) from 52 siphonophore taxa advanced several long standing questions about siphonophore biology. These include the relationships of the three historically recognised groups, Cystonectae, Physonectae, and Calycophorae. The cystonects were found to be sister to all other siphonophores, while the calycophorans were nested within physonects. The name Codonophora was given to this clade of physonects and calycophorans [@Dunn:2005dy].

Major questions remained after this early work, though. There was, in particular, little support for important deep relationships within Codonophora. Resolving deep relationships within Codonophora is key to resolving the evolution of several traits, including sexual systems (monoecy versus dioecy) or the gain and loss of particular zooids, such as palpons (Fig. 2). Here we present a broadly sampled phylogenomic analysis of Siphonophora, assessing transcriptomic data from 33 siphonophore species and 10 outgroup species (2 outgroups were subsequently excluded). Using 1,071 genes shared across species, we find strong support for several relationships within the siphonophore phylogeny. Using this phylogeny, we reconstruct the evolutionary history of characters central to their unique biology, including zooid type, life history traits, and habitat.

@@

#Mantle canal SIMMAP Setup
#mantle_data = cdata[which(!is.na(cdata$Mantle.Canal)),]
#mantle = mantle_data$Mantle.Canal
#names(mantle)=rownames(mantle_data)
#MantleTree =  drop.tip(ultratree, which(!(ultratree$tip.label %in% names(mantle))))
#make.simmap(MantleTree, mantle, nsim = 100, message=FALSE) -> mantle_sim
```

@@

```{r mantle, echo=F, message=F, warning=F,  fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of nectosome"}
#Simmap NECTOSOME
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# nectosome_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(nectosome_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
#densityMap(mantle_sim)
```
